---
title: "Assignment - Loading Data into a Data Frame"
author: "Jayden Jiang"
date: "2024-09-07"
output: html_document
---
### Library

```{r}
library(tidyverse)
library(dplyr)
```


### OVERVIEW

The data I chose to work on is "where People Go To Check The Weather", analyzed how people check the weather and the impact on traditional and online weather sources. The data was collected in April from 6th to 10th with 938 respondents.

The dataset was taken from: https://fivethirtyeight.com/features/weather-forecast-news-app-habits/

```{r}
# importing data from github

weather_data <- read.csv ("https://raw.githubusercontent.com/JaydeeJan/NBA-Prediction/main/weather-check.csv")
weather_data
```

```{r}
# Creating a subset data frame that to people who check weather daily
sub_weather <- weather_data %>% select(RespondentID, How.do.you.typically.check.the.weather., Age, )

sub_weather
```
```{r}
# rename the variables

colnames(sub_weather) <- c("Checkweather", "MethodOfChecking", "Age")
sub_weather

sum(sub_weather$MethodOfChecking == "The default weather app on your phone")

sum(sub_weather$MethodOfChecking == "A specific website or app (please provide the answer)")

sum(sub_weather$MethodOfChecking == "Local TV News")

sum(sub_weather$MethodOfChecking == "The Weather Channel")

sum(sub_weather$MethodOfChecking == "Internet search")

sum(sub_weather$MethodOfChecking == "Radio weather")

sum(sub_weather$MethodOfChecking == "Newsletter")


```

### Conclusion

From the finding, most people use the default weather app on their phone. 


### Session Info:
```{r}
sessionInfo()
```

